## PFCK expression in nontumor tissue
```{r DataSet, message = FALSE}
# Loading the dataset for analysis
source("PFCK_RCC_Tidy.R")
# Loading the simpleR package
library(simpleR)
```

### Percentage of PDL1+ nontumor cells
```{r PDL1_Nontumor_Percentage}
var <- Data$PDL1_Nontumor_Percentage
lab <- "PDL1+ nontumor cells, %"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Location of PDL1 positivity in nontumor cell structure
```{r PDL1_Nontumor_Location}
var <- Data$PDL1_Nontumor_Location
categorical.plot(var)
descriptive.categorical(var)
```

***

### H-score of PDL1 expression in nontumor cells
```{r PDL1_Nontumor_H}
var <- Data$PDL1_Nontumor_H
lab <- "PDL1 H-score in nontumor cells"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Percentage of PDL1+ inflammatory cells in stroma of nontumor tissue
```{r PDL1_Nontumor_Stroma_Percentage}
var <- Data$PDL1_Nontumor_Stroma_Percentage
lab <- "PDL1+ in stroma of nontumor tissue, %"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Total host response in nontumor tissue and stroma
```{r Host_Response_Nontumor}
var <- Data$Host_Response_Nontumor
categorical.plot(var)
descriptive.categorical(var)
```

***

### Number of FOXP3+ lymphocytes in nontumor tissue
```{r FOXP3_Nontumor_Lymphocytes}
var <- Data$PDL1_Nontumor_Stroma_Percentage
lab <- "FOXP3+ lymphocytes in nontumor tissue"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Number of FOXP3+ lymphocytes in stroma of nontumor tissue
```{r FOXP3_Nontumor_Stroma_Lymphocytes}
var <- Data$FOXP3_Nontumor_Stroma_Lymphocytes
lab <- "FOXP3+ lymphocytes in nontumor tissue stroma"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Intensity of FOXP3 staining in lymphocytes in nontumor tissue
```{r FOXP3_Nontumor_Lymphocytes_Intensity}
var <- Data$FOXP3_Nontumor_Lymphocytes_Intensity
categorical.plot(var)
descriptive.categorical(var)
```

***

### Number of FOXP3+ nontumor cells
```{r FOXP3_Nontumor}
var <- Data$FOXP3_Nontumor
lab <- "FOXP3+ nontumor cells"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Intensity of FOXP3 staining in nontumor cells
```{r FOXP3_Nontumor_Intensity}
var <- Data$FOXP3_Nontumor_Intensity
categorical.plot(var)
descriptive.categorical(var)
```

***

### Percentage of FOXP3+ nontumor cells
```{r FOXP3_Nontumor_Percentage}
var <- Data$FOXP3_Nontumor_Percentage
lab <- "FOXP3+ nontumor cells, %"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Number of CD8+ in nontumor tissue
```{r CD8_Nontumor}
var <- Data$CD8_Nontumor
lab <- "CD8+ in nontumor tissue"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Number of CD8+/Ki67+ lymphocytes in nontumor tissue
```{r CD8_Ki67_Nontumor}
var <- Data$CD8_Ki67_Nontumor
lab <- "CD8+/Ki67+ lymphocytes in nontumor tissue"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Number of CD8+ in stroma of nontumor tissue
```{r CD8_Nontumor_Stroma}
var <- Data$CD8_Nontumor_Stroma
lab <- "CD8+ in nontumor tissue stroma"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Number of CD8+/Ki67+ in stroma of nontumor tissue
```{r CD8_Ki67_Nontumor_Stroma}
var <- Data$CD8_Ki67_Nontumor_Stroma
lab <- "CD8+/Ki67+ in nontumor tissue stroma"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Percentage of Ki67+ nontumor cells
```{r Ki67_Nontumor_Percentage}
var <- Data$Ki67_Nontumor_Percentage
lab <- "Ki67+ non tumor cells, %"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***
