## PFCK expression in tumor tissue
```{r DataSet, message = FALSE}
# Loading the dataset for analysis
source("PFCK_RCC_Tidy.R")
# Loading the simpleR package
library(simpleR)
```

### Percentage of PDL1+ tumor cells
```{r PDL1_Tumor_Percentage}
var <- Data$PDL1_Tumor_Percentage
lab <- "PDL1+ tumor cells, %"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Location of PDL1 positivity in tumor cell structure
```{r PDL1_Tumor_Location}
var <- Data$PDL1_Tumor_Location
categorical.plot(var)
descriptive.categorical(var)
```

***

### H-score of PDL1 expression in tumor cells
```{r PDL1_Tumor_H}
var <- Data$PDL1_Tumor_H
lab <- "PDL1 H-score in tumor cells"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Percentage of PDL1+ inflammatory cells in stroma of tumor tissue
```{r PDL1_Tumor_Stroma_Percentage}
var <- Data$PDL1_Tumor_Stroma_Percentage
lab <- "PDL1+ in stroma of tumor tissue, %"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Total host response in tumor tissue and stroma
```{r Host_Response_Tumor}
var <- Data$Host_Response_Tumor
categorical.plot(var)
descriptive.categorical(var)
```

***

### Number of FOXP3+ lymphocytes in tumor tissue
```{r FOXP3_Tumor_Lymphocytes}
var <- Data$PDL1_Tumor_Stroma_Percentage
lab <- "FOXP3+ lymphocytes in tumor tissue"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Number of FOXP3+ lymphocytes in stroma of tumor tissue
```{r FOXP3_Tumor_Stroma_Lymphocytes}
var <- Data$FOXP3_Tumor_Stroma_Lymphocytes
lab <- "FOXP3+ lymphocytes in tumor tissue stroma"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Intensity of FOXP3 staining in lymphocytes in tumor tissue
```{r FOXP3_Tumor_Lymphocytes_Intensity}
var <- Data$FOXP3_Tumor_Lymphocytes_Intensity
categorical.plot(var)
descriptive.categorical(var)
```

***

### Number of FOXP3+ tumor cells
```{r FOXP3_Tumor}
var <- Data$FOXP3_Tumor
lab <- "FOXP3+ tumor cells"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Intensity of FOXP3 staining in tumor cells
```{r FOXP3_Tumor_Intensity}
var <- Data$FOXP3_Tumor_Intensity
categorical.plot(var)
descriptive.categorical(var)
```

***

### Percentage of FOXP3+ tumor cells
```{r FOXP3_Tumor_Percentage}
var <- Data$FOXP3_Tumor_Percentage
lab <- "FOXP3+ tumor cells, %"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Number of CD8+ in tumor tissue
```{r CD8_Tumor}
var <- Data$CD8_Tumor
lab <- "CD8+ in tumor tissue"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Number of CD8+/Ki67+ lymphocytes in tumor tissue
```{r CD8_Ki67_Tumor}
var <- Data$CD8_Ki67_Tumor
lab <- "CD8+/Ki67+ lymphocytes in tumor tissue"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Number of CD8+ in stroma of tumor tissue
```{r CD8_Tumor_Stroma}
var <- Data$CD8_Tumor_Stroma
lab <- "CD8+ in tumor tissue stroma"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Number of CD8+/Ki67+ in stroma of tumor tissue
```{r CD8_Ki67_Tumor_Stroma}
var <- Data$CD8_Ki67_Tumor_Stroma
lab <- "CD8+/Ki67+ in tumor tissue stroma"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***

### Percentage of Ki67+ tumor cells
```{r Ki67_Tumor_Percentage}
var <- Data$Ki67_Tumor_Percentage
lab <- "Ki67+ non tumor cells, %"
numerical.plot(var, label = lab)
descriptive.numerical(var)
```

***
