## PFCK expression in nontumor vs. tumor tissue
```{r DataSet, message = FALSE}
# Loading the dataset for analysis
source("PFCK_RCC_Tidy.R")
# Selecting only primary cases
Data <- subset(Data, Tissue == "Primary")
# Loading the simpleR package
library(simpleR)
# Sourcing functions for paired data
source("Paired_Data.R")
# Setting global options
knitr::opts_chunk$set(message = FALSE, warning = FALSE, fig.width = 9)
# Versus variables and labels
Data$Tissue_T <- "Tumor Tissue"
Data$Tissue_NT <- "Nontumor Tissue"
Tissue_Type <- factor(c(Data$Tissue_NT, Data$Tissue_T))
NT_lab <- "Nontumor tissue"
T_lab <- "Tumor tissue"
```

### Percentage of PDL1+ nontumor vs. tumor cells
```{r PDL1_NvT_Percentage}
NT_var <- log10(Data$PDL1_Nontumor_Percentage + 1)
T_var <- log10(Data$PDL1_Tumor_Percentage + 1)
yaxis <- "PDL1+ cells, log %"
numerical.group.plot2(NT_var, T_var, NT_lab, T_lab, labmain = yaxis)
```

***

### Location of PDL1 positivity in nontumor vs. tumor cell structure
```{r PDL1_NvT_Location}
NT_var <- Data$PDL1_Nontumor_Location
T_var <- Data$PDL1_Tumor_Location
NvT <- unlist(list(NT_var, T_var))
labx <- "Location of PDL1 positivity"
categorical.group.plot2(NvT, Tissue_Type, xlab = labx)
```

***

### H-score of PDL1 expression in nontumor vs. tumor cells
```{r PDL1_NvT_H}
NT_var <- log10(Data$PDL1_Nontumor_H + 1)
T_var <- log10(Data$PDL1_Tumor_H + 1)
yaxis <- "PDL1, log H-score"
numerical.group.plot2(NT_var, T_var, NT_lab, T_lab, labmain = yaxis)
```

***

### Percentage of PDL1+ inflammatory cells in stroma of nontumor vs. tumor tissue
```{r PDL1_NvT_Stroma_Percentage}
NT_var <- log10(Data$PDL1_Nontumor_Stroma_Percentage + 1)
T_var <- log10(Data$PDL1_Tumor_Stroma_Percentage + 1)
yaxis <- "PDL1+ in stroma, log %"
numerical.group.plot2(NT_var, T_var, NT_lab, T_lab, labmain = yaxis)
```

***

### Total host response in nontumor vs. tumor tissue and stroma
```{r Host_Response_NvT}
NT_var <- Data$Host_Response_Nontumor
T_var <- Data$Host_Response_Tumor
NvT <- unlist(list(NT_var, T_var))
labx <- "Total host response"
categorical.group.plot2(NvT, Tissue_Type, xlab = labx)
```

***

### Number of FOXP3+ lymphocytes in nontumor vs. tumor tissue
```{r FOXP3_NvT_Lymphocytes}
NT_var <- log10(Data$FOXP3_Nontumor_Lymphocytes + 1)
T_var <- log10(Data$FOXP3_Tumor_Lymphocytes + 1)
yaxis <- "FOXP3+ lymphocytes, log"
numerical.group.plot2(NT_var, T_var, NT_lab, T_lab, labmain = yaxis)
```

***

### Number of FOXP3+ lymphocytes in stroma of nontumor vs. tumor tissue
```{r FOXP3_NvT_Stroma_Lymphocytes}
NT_var <- log10(Data$FOXP3_Nontumor_Stroma_Lymphocytes + 1)
T_var <- log10(Data$FOXP3_Tumor_Stroma_Lymphocytes + 1)
yaxis <- "FOXP3+ lymphocytes in stroma, log"
numerical.group.plot2(NT_var, T_var, NT_lab, T_lab, labmain = yaxis)
```

***

### Intensity of FOXP3 staining in lymphocytes in nontumor vs. tumor tissue
```{r FOXP3_NvT_Lymphocytes_Intensity}
NT_var <- Data$FOXP3_Nontumor_Lymphocytes_Intensity
T_var <- Data$FOXP3_Tumor_Lymphocytes_Intensity
NvT <- unlist(list(NT_var, T_var))
labx <- "FOXP3 staining intensity in lymphocytes"
categorical.group.plot2(NvT, Tissue_Type, xlab = labx)
```

***

### Number of FOXP3+ nontumor vs. tumor cells
```{r FOXP3_NvT, eval = FALSE}
NT_var <- log10(Data$FOXP3_Nontumor + 1)
T_var <- log10(Data$FOXP3_Tumor + 1)
yaxis <- "FOXP3+ cells, log"
numerical.group.plot2(NT_var, T_var, NT_lab, T_lab, labmain = yaxis)
```

No plots or comparisons are generated due to the fact that all observations had the same values.

***

### Intensity of FOXP3 staining in nontumor vs. tumor cells
```{r FOXP3_NvT_Intensity}
NT_var <- Data$FOXP3_Nontumor_Intensity
T_var <- Data$FOXP3_Tumor_Intensity
NvT <- unlist(list(NT_var, T_var))
labx <- "FOXP3 staining intensity"
categorical.group.plot2(NvT, Tissue_Type, xlab = labx)
```

***

### Percentage of FOXP3+ nontumor vs. tumor cells
```{r FOXP3_NvT_Percentage, eval = FALSE}
NT_var <- log10(Data$FOXP3_Nontumor_Percentage + 1)
T_var <- log10(Data$FOXP3_Tumor_Percentage + 1)
yaxis <- "FOXP3+ cells, % log"
numerical.group.plot2(NT_var, T_var, NT_lab, T_lab, labmain = yaxis)
```

No plots or comparisons are generated due to the fact that all observations had the same value.

***

### Number of CD8+ in nontumor vs. tumor tissue
```{r CD8_NvT}
NT_var <- log10(Data$CD8_Nontumor + 1)
T_var <- log10(Data$CD8_Tumor + 1)
yaxis <- "CD8+ cells, log"
numerical.group.plot2(NT_var, T_var, NT_lab, T_lab, labmain = yaxis)
```

***

### Number of CD8+/Ki67+ lymphocytes in nontumor vs. tumor tissue
```{r CD8_Ki67_NvT}
NT_var <- Data$CD8_Ki67_Nontumor
T_var <- Data$CD8_Ki67_Tumor
yaxis <- "CD8+/Ki67+ lymphocytes, log"
numerical.group.plot2(NT_var, T_var, NT_lab, T_lab, labmain = yaxis)
```

***

### Number of CD8+ in stroma of nontumor vs. tumor tissue
```{r CD8_NvT_Stroma}
NT_var <- Data$CD8_Nontumor_Stroma
T_var <- Data$CD8_Tumor_Stroma
yaxis <- "CD8+ cells in stroma, log"
numerical.group.plot2(NT_var, T_var, NT_lab, T_lab, labmain = yaxis)
```

***

### Number of CD8+/Ki67+ in stroma of nontumor vs. tumor tissue
```{r CD8_NvT_Tumor_Stroma}
NT_var <- Data$CD8_Ki67_Nontumor_Stroma
T_var <- Data$CD8_Ki67_Tumor_Stroma
yaxis <- "CD8+/Ki67+ cells in stroma, log"
numerical.group.plot2(NT_var, T_var, NT_lab, T_lab, labmain = yaxis)
```

***

### Percentage of Ki67+ nontumor vs. tumor cells
```{r Ki67_NvT_Percentage}
NT_var <- Data$Ki67_Nontumor_Percentage
T_var <- Data$Ki67_Tumor_Percentage
yaxis <- "Ki67+ cells, log %"
numerical.group.plot2(NT_var, T_var, NT_lab, T_lab, labmain = yaxis)
```

***
