## PFCK expression in primary vs. metastatic tumors
```{r DataSet, message = FALSE}
# Loading the dataset for analysis
source("PFCK_RCC_Tidy.R")
# Loading the simpleR package
library(simpleR)
# Sourcing functions for paired data
source("Paired_Data.R")
# Setting global options
knitr::opts_chunk$set(message = FALSE, warning = FALSE, fig.width = 9)
# Versus variables
vary <- Data$Tissue
```

### Percentage of PDL1+ tumor cells
```{r PDL1_PvM_Percentage}
varx <- log10(Data$PDL1_Tumor_Percentage + 1)
yaxis <- "PDL1+ cells, log %"
numerical.group.plot(varx, vary, lab = yaxis)
```

***

### Location of PDL1 positivity in tumor cell structure
```{r PDL1_PvM_Location}
varx <- Data$PDL1_Tumor_Location
categorical.group.plot2(varx, vary)
```

***

### H-score of PDL1 expression in tumor cells
```{r PDL1_PvM_H}
varx <- log10(Data$PDL1_Tumor_H + 1)
yaxis <- "PDL1, log H-score"
numerical.group.plot(varx, vary, lab = yaxis)
```

***

### Percentage of PDL1+ inflammatory cells in stroma of tumor tissue
```{r PDL1_PvM_Stroma_Percentage}
varx <- log10(Data$PDL1_Tumor_Stroma_Percentage + 1)
yaxis <- "PDL1+ inflammatory cells in stroma, log %"
numerical.group.plot(varx, vary, lab = yaxis)
```

***

### Total host response in tumor tissue and stroma
```{r Host_Response_PvM}
varx <- Data$Host_Response_Tumor
categorical.group.plot2(varx, vary)
```

***

### Number of FOXP3+ lymphocytes in tumor tissue
```{r FOXP3_PvM_Lymphocytes}
varx <- log10(Data$FOXP3_Tumor_Lymphocytes + 1)
yaxis <- "FOXP3+ lymphocytes, log"
numerical.group.plot(varx, vary, lab = yaxis)
```

***

### Number of FOXP3+ lymphocytes in stroma of tumor tissue
```{r FOXP3_PvM_Stroma_Lymphocytes}
varx <- log10(Data$FOXP3_Tumor_Stroma_Lymphocytes + 1)
yaxis <- "FOXP3+ lymphocytes in stroma, log"
numerical.group.plot(varx, vary, lab = yaxis)
```

***

### Intensity of FOXP3 staining in lymphocytes in tumor tissue
```{r FOXP3_PvM_Lymphocytes_Intensity}
varx <- Data$FOXP3_Tumor_Lymphocytes_Intensity
categorical.group.plot2(varx, vary)
```

***

### Number of FOXP3+ tumor cells
```{r FOXP3_PvM}
varx <- log10(Data$FOXP3_Tumor + 1)
yaxis <- "FOXP3+ tumor cells, log"
numerical.group.plot(varx, vary, lab = yaxis)
```

***

### Intensity of FOXP3 staining in tumor cells
```{r FOXP3_PvM_Intensity}
varx <- Data$FOXP3_Tumor_Intensity
categorical.group.plot2(varx, vary)
```

***

### Percentage of FOXP3+ tumor cells
```{r FOXP3_PvM_Percentage, eval = FALSE}
varx <- log10(Data$FOXP3_Tumor_Percentage + 1)
yaxis <- "FOXP3+ tumor cells, % log"
numerical.group.plot(varx, vary, lab = yaxis)
```

**Plots not generated:** all observations were in the same group.

***

### Number of CD8+ in tumor tissue
```{r CD8_PvM}
varx <- log10(Data$CD8_Tumor + 1)
yaxis <- "CD8+ tumor cells, log"
numerical.group.plot(varx, vary, lab = yaxis)
```

***

### Number of CD8+/Ki67+ lymphocytes in tumor tissue
```{r CD8_Ki67_PvM}
varx <- log10(Data$CD8_Ki67_Tumor + 1)
yaxis <- "CD8+/Ki67+ lymphocytes, log"
numerical.group.plot(varx, vary, lab = yaxis)
```

***

### Number of CD8+ in stroma of tumor tissue
```{r CD8_PvM_Stroma}
varx <- log10(Data$CD8_Tumor_Stroma + 1)
yaxis <- "CD8+ cells in stroma, log"
numerical.group.plot(varx, vary, lab = yaxis)
```

***

### Number of CD8+/Ki67+ in stroma of tumor tissue
```{r CD8_PvM_Tumor_Stroma}
varx <- log10(Data$CD8_Ki67_Tumor_Stroma + 1)
yaxis <- "CD8+/Ki67+ cells in stroma, log"
numerical.group.plot(varx, vary, lab = yaxis)
```

***

### Percentage of Ki67+ tumor cells
```{r Ki67_PvM_Percentage}
varx <- log10(Data$Ki67_Tumor_Percentage + 1)
yaxis <- "Ki67+ tumor cells, log %"
numerical.group.plot(varx, vary, lab = yaxis)
```

***
